Allee Effect and Cultural Evolution

### 2015-06-20 manuscript/draft.tex
Minor Update

Several behavioural traits are expected to show such density dependence. For example, behaviour linked to the exploitation of some limited resources are expected to exhibit decline when the density exceeds a critical threshold (i.e carrying capacity). Thus novel optimal variants are likely to spread rapidly when the trait is rare, but as it approaches carrying capacity, the  beneficial effects will start to decline, the payoff will become smaller, and eventually rarer suboptimal variants might be preferred (see Lake and Crema \citeyear{lake_and_crema_2012} for an extensive analysis).

>>>>

Several behavioural traits are expected to show such a density dependence. For example, behaviour linked to the exploitation of limited resources will exhibit a decline in payoff when density exceeds a critical threshold (i.e carrying capacity). In this case a new optimal variant is likely to spread rapidly when the it is rare, but as the number of individuals possessing it approaches carrying capacity, its beneficial effects will start to decline, the payoff will decrease, and eventually rarer suboptimal variants might be preferred (see Lake and Crema \citeyear{lake_and_crema_2012} for an extensive analysis).
